---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
                      collapse = TRUE,
                      comment = "#>",
                      dpi = 300, 
                      fig.path = "man/figures/README-",
                      out.width = "100%",
                      warning = FALSE,
                      message = FALSE
                  )
```

# calibcurve

<!-- badges: start -->
<!-- badges: end -->

`calibcurve` implements functions to compute true and predicted probabilities
and visualise a calibration curve, aka reliability diagram ([Niculescu-Mizil &
Caruana, 2005](https://dl.acm.org/doi/10.1145/1102351.1102430)).

* `calibcurve` is powered by the `[yardstick](https://yardstick.tidymodels.org/index.html)`'s 
  infrastructure and its implementation of related curve metrics.
  
* `calibcurve` borrowed some ideas from sklearn's [calibration](https://scikit-learn.org/stable/modules/generated/sklearn.calibration.calibration_curve.html#sklearn.calibration.calibration_curve) module.

## Installation

You can install the released version of calibcurve from
[CRAN](https://CRAN.R-project.org) with:

``` r
# install.packages("calibcurve")
# Not yet!
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chuvanan/calibcurve")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(calibcurve)
library(magrittr)
library(ggplot2)

data(two_class_example, package = "yardstick")
head(two_class_example)

two_class_example %>%
    calibration_curve(truth, Class1)

two_class_example %>%
    calibration_curve(truth, Class1) %>%
    autoplot()
```

## Code of Conduct

Please note that the calibcurve project is released with a [Contributor Code of
Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By
contributing to this project, you agree to abide by its terms.
